Lens Modeling in \sw

### 2013-11-25 text/tex/outlook.tex

As seen in \secref{tests.t1}, volunteers fail mostly in two situations:
when to identify an arclike structre while placing the points
and in 5 image configurations, that are quite symmetric, then to identify the correct ordering of the points.

@@

The second can be made less by better training (introduce the ruler), maybe more filters help too?

We hope that those problems are also taken care of when staring collaborative modelling. (Already in progress)
Basics are available ('revise functionality') but better community tools would help (having overview, comparison between different models ect...)

>>>>

As seen in \secref{tests.t1}, volunteers fail mostly in two situations:
when to identify an arclike structure while placing the points
and in 5 image configurations, that are quite symmetric, then to identify the correct ordering of the points.

@@

The second can be made less by better training (introduce the ruler), may be more filters help too?

We hope that those problems are also taken care of when staring collaborative modeling. (Already in progress)
Basics are available ('revise functionality') but better community tools would help (having overview, comparison between different models ect...)
